\documentclass[11pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=0.5in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{tcolorbox}
\pagenumbering{gobble}

\definecolor{solanapurple}{RGB}{20, 241, 149}
\definecolor{darkgray}{RGB}{40, 40, 40}

\titleformat{\section}{\large\bfseries\color{darkgray}}{\thesection}{1em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{darkgray}}{\thesubsection}{1em}{}

\title{\textbf{Technical Implementation Roadmap v2} \\ \large Auxin Automata --- The Agentic Infrastructure API for Autonomous Hardware}
\author{Edwin Redhead \& Tara Kasayapanand}
\date{Colosseum Frontier Hackathon Sprint}

\begin{document}
\maketitle

\begin{abstract}
Comprehensive engineering checklist for the Auxin Automata MVP. Bridges high-frequency telemetry, Solana M2M micropayments, and immutable compliance. Sequential phases and parallel tracks, with explicit fallback paths to de-risk hardware-dependent deliverables.
\end{abstract}

\vspace{1em}

\section{Phase 0: Repository \& Tooling Bootstrap (Sequential)}
\textit{Foundation work. Half a day; skipping it costs days later.}
\begin{itemize}
    \item \textbf{0.1 Monorepo:} GitHub repo \texttt{auxin-automata} with workspaces \texttt{/sdk}, \texttt{/programs}, \texttt{/edge}, \texttt{/dashboard}, \texttt{/twin}, \texttt{/docs}, \texttt{/scripts}.
    \item \textbf{0.2 Git Hygiene:} Protected \texttt{main}, conventional commits, PR template, CODEOWNERS splitting Edwin/Tara ownership.
    \item \textbf{0.3 CI Pipeline:} GitHub Actions for Python (\texttt{ruff}, \texttt{pytest}), Anchor (\texttt{anchor test}), Next.js build/lint.
    \item \textbf{0.4 Secrets:} \texttt{.env.example} per workspace, Doppler/1Password CLI, \texttt{gitleaks} pre-commit hook.
    \item \textbf{0.5 Project Board:} GitHub Projects mirroring this roadmap with W1--W5 milestones.
    \item \textbf{0.6 Dev Container:} \texttt{devcontainer.json} pinning Python 3.11, Node 20, Rust, Solana CLI, Anchor versions.
\end{itemize}

\section{Phase 1: Foundation \& Mock Infrastructure (Sequential)}
\textit{Full end-to-end loop must run on a laptop with no hardware by end of Week 1.}

\subsection*{1A: SDK Core (\texttt{auxin-sdk})}
\begin{itemize}
    \item \textbf{1A.1 Package:} \texttt{pyproject.toml}, \texttt{src/} layout, \texttt{uv}/\texttt{poetry}. This package proves hardware-agnosticism to judges.
    \item \textbf{1A.2 Wallet Module:} \texttt{HardwareWallet} wrapping \texttt{solders}: keypair load, sign\_transaction, balance, devnet airdrop helper.
    \item \textbf{1A.3 Telemetry Schema:} Pydantic \texttt{TelemetryFrame} (timestamp, joint\_positions, velocities, torques, end\_effector\_pose, anomaly\_flags). Single source of truth.
    \item \textbf{1A.4 Hashing Utility:} Deterministic canonical-JSON SHA-256 hasher with determinism unit tests.
    \item \textbf{1A.5 Abstract \texttt{TelemetrySource}:} ABC with \texttt{async stream()}; concrete: \texttt{MockSource}, \texttt{TwinSource}, \texttt{ROS2Source}. Agnosticism contract.
    \item \textbf{1A.6 Logging:} \texttt{structlog} JSON output, request IDs propagated through async calls.
    \item \textbf{1A.7 Test Suite:} \texttt{pytest}, coverage $\geq 80\%$.
\end{itemize}

\subsection*{1B: Mock Generators}
\begin{itemize}
    \item \textbf{1B.1 Keypair Bootstrap:} Generate, persist to \texttt{\textasciitilde/.config/auxin/hardware.json}, airdrop 2 Devnet SOL, verify.
    \item \textbf{1B.2 Mock Kinematics:} Drifting joint angles via sine/cosine + noise; 6 DoF; 10\,Hz default.
    \item \textbf{1B.3 Anomaly Injection:} Configurable torque spikes every 10--15 frames; obstacle flags.
    \item \textbf{1B.4 Vision Fixtures:} \texttt{/fixtures/images/} with $\sim$20 labelled images (clear/obstacle); sampler returns path + ground truth.
    \item \textbf{1B.5 Replay Mode:} Record sessions to JSONL, replay deterministically for debugging and demo reproducibility.
\end{itemize}

\subsection*{1C: Digital Twin Fallback (Critical De-risk)}
\textit{Insurance policy. If physical arm slips, the twin carries the demo video.}
\begin{itemize}
    \item \textbf{1C.1 PyBullet Scene:} Load Franka Panda or UR5 URDF, table, obstacle box.
    \item \textbf{1C.2 Demo Trajectory:} Pre-scripted IK pick-and-place loop on repeat.
    \item \textbf{1C.3 \texttt{TwinSource}:} Extract joint states from PyBullet at 10\,Hz, conform to schema.
    \item \textbf{1C.4 Headless Render:} Off-screen MP4 render plus websocket frame feed for the dashboard.
    \item \textbf{1C.5 Source Switch:} \texttt{AUXIN\_SOURCE=mock|twin|ros2} flag toggles source --- proves agnosticism in code.
\end{itemize}

\subsection*{1D: Gemini Safety Oracle}
\begin{itemize}
    \item \textbf{1D.1 Async Client:} Wrapper around \texttt{google-generativeai} with retry, timeout, exponential backoff.
    \item \textbf{1D.2 Structured Output:} JSON schema enforcement: \texttt{\{action\_approved: bool, reason: str, confidence: float\}}.
    \item \textbf{1D.3 Prompt Versioning:} Prompts in \texttt{/sdk/prompts/} as versioned files; loader logs version per call.
    \item \textbf{1D.4 Eval Harness:} Run oracle against labelled fixtures; assert $\geq 90\%$ accuracy; CI fails on regression.
    \item \textbf{1D.5 Cost/Latency Metrics:} Log token counts and latency, expose Prometheus-style for the dashboard.
    \item \textbf{1D.6 Local Fallback Heuristic:} On Gemini failure or $>$2\,s timeout, fall back to torque + obstacle flag rule so demo never stalls.
\end{itemize}

\section{Phase 2: Core Architecture Development (Parallel)}
\textit{Three pillars in parallel. Edwin and Tara split tracks. Each ends fully testable in isolation.}

\subsection*{Track A: Blockchain (Solana / Anchor / Rust)}
\begin{itemize}
    \item \textbf{2A.1 Anchor Workspace:} Scaffold \texttt{agentic\_hardware\_bridge}, Anchor 0.30+, Devnet via Helius RPC.
    \item \textbf{2A.2 PDA Spec:} Markdown design doc for \texttt{HardwareAgent}, \texttt{ComputeProvider}, \texttt{ComplianceLog} accounts; review before coding.
    \item \textbf{2A.3 \texttt{initialize\_agent}:} Creates HardwareAgent PDA storing pubkey, compute\_budget, provider whitelist.
    \item \textbf{2A.4 \texttt{stream\_compute\_payment}:} Transfers lamports to whitelisted provider; per-tx cap; rolling-window rate limit; emits \texttt{ComputePaymentEvent}.
    \item \textbf{2A.5 \texttt{log\_compliance\_event}:} Accepts hashed telemetry + severity enum; emits \texttt{ComplianceEvent}.
    \item \textbf{2A.6 \texttt{update\_provider\_whitelist}:} Authority-gated provider add/remove.
    \item \textbf{2A.7 Custom Errors:} \texttt{\#[error\_code]} enum: unauthorized, budget exceeded, rate limit, invalid provider.
    \item \textbf{2A.8 TS Test Suite:} Happy path, every error path, event listener verification, rate-limit boundaries, multi-agent isolation.
    \item \textbf{2A.9 Localnet CI Gate:} \texttt{anchor test} clean.
    \item \textbf{2A.10 Devnet Deploy Script:} Idempotent, program ID pinned, IDL upload, post-deploy smoke test.
    \item \textbf{2A.11 Client Generation:} Generate TS and Python clients from IDL; Python client consumed by \texttt{auxin-sdk}.
    \item \textbf{2A.12 Security Pass:} \texttt{cargo-audit}; manual checklist for signer checks, CPI safety, overflow, account ownership.
\end{itemize}

\subsection*{Track B: Hardware \& Edge (Jetson / ROS2)}
\textit{Gated on Superteam grant. Twin (1C) must be production-ready before this track starts.}
\begin{itemize}
    \item \textbf{2B.1 Jetson Provision:} Flash Orin Nano with JetPack 6, SSH, swap, Docker.
    \item \textbf{2B.2 ROS2 Humble:} Containerised install; verify \texttt{ros2 topic list}.
    \item \textbf{2B.3 Arm Driver:} Target arm (myCobot 280 recommended); install vendor driver; verify joint\_state publication.
    \item \textbf{2B.4 URDF Alignment:} Match physical arm URDF to digital twin so visualisations and code are interchangeable.
    \item \textbf{2B.5 Telemetry Bridge Node:} Subscribes \texttt{/joint\_states}, throttles to 2\,Hz, publishes to internal queue consumed by \texttt{ROS2Source}.
    \item \textbf{2B.6 Watchdog Node:} Independent torque-monitor, calls \texttt{/emergency\_stop}; runs without network or Solana.
    \item \textbf{2B.7 Camera Node:} USB camera frames for the oracle's vision check.
    \item \textbf{2B.8 systemd Services:} Bridge, watchdog, SDK runner auto-start on boot.
    \item \textbf{2B.9 Remote Logging:} Forward Jetson logs to Grafana Loki for laptop-side debugging.
\end{itemize}

\subsection*{Track C: Dashboard (Next.js)}
\begin{itemize}
    \item \textbf{2C.1 Next.js 14 Scaffold:} App router, TS strict, Tailwind, shadcn/ui, lucide-react. Mechafloral design tokens.
    \item \textbf{2C.2 Layout Shell:} Header (status, agent pubkey), three-column responsive grid.
    \item \textbf{2C.3 Telemetry Card:} Live joint angles + torque sparklines (Recharts); colour-shifts on anomaly.
    \item \textbf{2C.4 M2M Payment Ticker:} Scrolling \texttt{ComputePaymentEvent} list with Explorer links.
    \item \textbf{2C.5 Compliance Log Table:} Sortable \texttt{ComplianceEvent} table with severity badges and hash copy-button.
    \item \textbf{2C.6 \texttt{useProgramEvents} Hook:} \texttt{@solana/web3.js} \texttt{onLogs} subscription; reconnect, dedup, cleanup.
    \item \textbf{2C.7 Twin Viewport:} react-three-fiber canvas rendering URDF, fed by PyBullet websocket or live ROS2 bridge.
    \item \textbf{2C.8 State Management:} Zustand store; clean network/UI separation.
    \item \textbf{2C.9 Empty/Error/Loading:} Every panel handles all three; no white screens during the demo.
    \item \textbf{2C.10 Vercel Deploy:} Preview deploys per PR; production on \texttt{main}.
\end{itemize}

\section{Phase 3: Bridge \& Integration (Sequential)}
\textit{Run twice: digital twin first (end of Week 2), then physical arm (Week 3--4).}
\begin{itemize}
    \item \textbf{3.1 Bridge Service:} Long-running async process: pull telemetry $\rightarrow$ run oracle $\rightarrow$ if approved sign payment, if denied sign compliance log $\rightarrow$ push to dashboard ws.
    \item \textbf{3.2 Source Switch:} Bridge picks \texttt{TwinSource} or \texttt{ROS2Source} via env; identical downstream code path. Agnosticism proof.
    \item \textbf{3.3 Submission Layer:} Anchor client wrapper with priority fee logic, blockhash refresh, retry on \texttt{BlockhashNotFound}, idempotency keys.
    \item \textbf{3.4 Backpressure:} On submission queue growth, drop low-severity telemetry; never drop compliance events.
    \item \textbf{3.5 \texttt{/healthz}:} Source status, last successful tx, last oracle latency.
    \item \textbf{3.6 E2E Test (Twin):} Inject anomaly; assert compliance event on Devnet within 5\,s.
    \item \textbf{3.7 E2E Test (Hardware):} Same script against physical arm.
    \item \textbf{3.8 Demonstrated Action 1 --- M2M Economy:} Clear path $\rightarrow$ Gemini approves $\rightarrow$ payment streamed $\rightarrow$ dashboard updates.
    \item \textbf{3.9 Demonstrated Action 2 --- Compliance Log:} Torque spike $\rightarrow$ watchdog halts arm $\rightarrow$ telemetry hashed $\rightarrow$ on-chain log $\rightarrow$ red event in dashboard.
    \item \textbf{3.10 Failure Drill:} Kill the network mid-demo; verify watchdog still halts the arm locally. This is the safety talking point.
\end{itemize}

\section{Phase 4: Hardening, Observability \& Submission (Sequential)}
\textit{Move from "works on my machine" to "judges can clone and run it."}
\begin{itemize}
    \item \textbf{4.1 Observability:} Prometheus metrics from the bridge (tx count, oracle latency, anomaly count); Grafana dashboard JSON checked in.
    \item \textbf{4.2 Error Tracking:} Sentry on bridge and dashboard.
    \item \textbf{4.3 Reproducibility:} \texttt{make demo} spins up the entire twin-mode stack via docker-compose in $<$60\,s.
    \item \textbf{4.4 Documentation:} Root \texttt{README.md} with architecture diagram, quickstart, deployed program IDs, env var reference, troubleshooting. Per-workspace READMEs.
    \item \textbf{4.5 Architecture Diagram:} Excalidraw or Mermaid embedded in root README.
    \item \textbf{4.6 License:} Apache 2.0 (Public Goods Award eligible) at repo root and per workspace.
    \item \textbf{4.7 Demo Recording:} Split-screen capture: arm (or twin) left, dashboard right, terminal showing live tx hashes.
    \item \textbf{4.8 Devnet Address Sheet:} Single page: program ID, agent pubkey, provider pubkey, sample tx signatures with Explorer links.
    \item \textbf{4.9 Final Submission:} Colosseum portal --- video, GitHub link, deployed addresses, pitch deck, team bios.
\end{itemize}

\end{document}